Dependent Object Types

### 2012-08-06 article.tex
really rough sketch of the subst lemma

By the substitution lemma, ${\subst {v_2} {x_i} {t_i}} \in \rele
{k-\max(j_1,j_2)-1} {\Gamma_{12}} {s_{12}} {T}$. Supposing,
$\reductionl {\subst {v_2} {x_i} {t_i}} {s_{12}} {t'} {s'} {j_3}$,
with $j_1 + j_2 + j_3 + 1 = k$, this completes the case by
monotonicity of $\mathcal{V}$.

@@

\todo{statement and proof}

>>>>

By the substitution lemma, ${\subst {v_2} {x_i} {t_i}} \in \rele
{k-\max(j_1,j_2)-1} {\Gamma_{12}} {s_{12}} {T}$. Supposing,
$\reductionl {\subst {v_2} {x_i} {t_i}} {s_{12}} {t'} {s'} {j_3}$,
with $j_1 + j_2 + j_3 + 1 = j$, this completes the case, eventually by
monotonicity of $\mathcal{V}$.

@@

The substitution lemma states that if (1) $v_2 \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {T_2}$ and (2) $t \in \rele {k_1} {\Gamma_1
  \envplus{{x_i} : S}} {s_1} T$ and (3) $\Gamma \ts {T_2} \sub S$ with
$\Gamma$ included in $\Gamma_1$ and $\Gamma_{12}$ included in
$\Gamma_1$ and $s_{12}$ included in $s_1$, then $\subst {v_2} {x_i}
{t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12}} {s_{12}} T$.

\begin{proofsketch}
By (1) and (3), it should hold that (4) $v_2 \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {S}$. Since (2) holds, it should also hold that
${t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12} \envplus{{x_i} : S}}
{s_{12}} T$ by monotonicity of the logical relation on all
subscripts. Then, we can instantiate $x_i$ in the complete store to
map to what $v_2$ maps to. This should be fine by (4) and
monotonicity. Thus, ${t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12}
  \envplus{{x_i} : S}} {s_{12} \envplus{{x_i} \mapsto s_{12}(v)}}
T$. This implies what needs to be shown.
\end{proofsketch}
